---
title: "HW 1 - Intro to R"
author: Nicholas Walker
date: 09/15/23
output: html_document
---

Put your R code and explanations below each question in this markdown file and submit the knitted `html` file to Canvas.

#### President ages

1. Create a vector `ages` containing the age (at inauguration) of the ten most recent Presidents. Using the names function add last names to the values of this vector. Create another vector `year` containing the year at inauguration of these ten Presidents.

1. Find the `mean`, `min`, and `maximum` age of these 10 Presidents.

1. Using logical operations, create a new vector `age_young` with the ages of the Presidents younger than 50.

1. Create a vector `age_after_1975`of the ages of the Presidents inaugurated after 1975.

1. Using the `plot()` function, plot the inauguration `year` against the `age` for these 10 Presidents (x=`age`, y=`ear`). Do you see any pattern in this graph? Please provide your observation in **bold**.

#work
```{r}
ages <- c(78,70,47,54,46,64,69,52,61,56)
names(ages) <- c("Biden","Trump","Obama","Bush","Clinton","Bush","Reagan","Carter","Ford","Nixon")
year <- c(2021,2017,2009,2001,1993,1989,1981,1977,1974,1969)

mean(ages)
min(ages)
max(ages)

age_after_1975 <- ages[ages>1975]

plot(year,ages)
```
**I've noticed that majority of presidents start over 55. Other than that it seems pretty random**

#### Writing hand and gender

For a class of 20 students, the following vectors store their gender (`F` or `M`) and writing hand (`L` or `R`). 

```{r}
gender <- c("M","F","F","M","F","M","F","F","M","F","M","F","M","F","F","F","M","F","F","F")
hand <- c("R","R","L","R","R","R","R","L","R","R","R","R","R","R","L","L","L","R","R","R")
```

1. Using `table()` fucntion, construct and display a frequency table of writing hand. Type `?table` in console and press `Enter` to see how `table()` works.

1. Using `barplot()` function, construct a bar plot of these writing hand frequencies. Type `?barplot()` in console and press `Enter` to see how `barplot()` works.

1. Using logical operations, create a vector of the writing hand of the women and another vector of the writing hand the men.

#work
```{r}
table(gender, hand)
barplot(table(gender, hand))

names(hand) <- c(gender)

wHand_Women <- hand[names(hand)=='F']
wHand_Men <-  hand[names(hand)=='M']

```

#### Functions and vector operations

1. Write a function called `from_F_C()` which takes the temperature value in degrees Fahrenheit as an input and outputs its corresponding value in degrees Celsius. Test your function for 32F and 95F. 

2. It is well known that $\sin(1)$ (the value of sine function at 1)  can be approximated by the sum
\[
1 - \frac{1}{3!} + \frac{1}{5!} - \frac{1}{7!} + … + (-1)^n\frac{1}{(2n+1)!}
\]
where $n$ is a non-negative integer and $k! = 1 \cdot 2\cdots k$ ($k$ factorial). Let n be in the range 0,...,7. Using the `for` loop and the conditional `if`, find the smallest value of $n$ such that
\[
|Error| = |1 - \frac{1}{3!} + \frac{1}{5!} - \frac{1}{7!} + … + (-1)^n\frac{1}{(2n+1)!} - \sin(1)| < 0.0001
\]
When the smallest such $n$ is found, print it on the screen and use `break` command to exit the `for` loop. Also, using this $n$, print your approximation of the value of $\sin(1)$. 
_Note_: In R, $\sin(1)$ is `sin(1)` and $k!$ is `factorial(k)`. 

#work
```{r}
from_F_C <- function(temp){
  temp_C <- (temp-32)*5/9
  return(temp_C)
}

print(from_F_C(32))
print(from_F_C(95))

for(x in 0:7){
  if()
}


```

